---
title: "Weight of Fish"
author: "Karina Toribio"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

# Predicting Fish Weight
## Get data
```{r}
fishData=read.csv("Fish.csv")
```


## Perch
```{r}
perch = filter(fishData, Species == "Perch")
```

### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=perch,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```

The best two variables to predict weight are height and width. 

### Best Two regressor model

```{r}
perchModel=lm(Weight~Height+Width, data=perch)
summary(perchModel)
```

The best model for the adjusted r square for perch was 0.94. 

## Pike
```{r}
pike = filter(fishData, Species == "Pike")
```

### Best Models

```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=pike,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```

The best two variables for pike are length1 and length3.

### Best Two regressor model

```{r}
pikeModel=lm(Weight~Length1+Length3, data=pike)
summary(pikeModel)
```

The best model for the adjusted r square for pike is 0.9649.

## Roach

```{r}
Roach = filter(fishData, Species == "Roach")
```

### Best Models

```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=Roach,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```
The best two variables for roach are length3 and width.

### Best Two regressor model

```{r}
RoachModel=lm(Weight~Length3+Width, data=Roach)
summary(RoachModel)
```
The best model for the adjusted r square for Roach is 0.8482

## Final Summary Statements
Out of all the data we tried, from lowest to highest, roach is at 0.8482, then perch at 0.94 , and pike at 0.96. This is concluding that pike is the best out of the 3 models that we did since it was the highest value. 
